---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

`sentimental` : Tools to Work with the [`text-processing.com`](text-processing.com) API.

If you have modest NLP needs, this API package provides an alternative to getting Java-based packages to work or performing processing on your local system.

NOTE: There is a limit of 1,000 API calls per day imposed by the API.

The following functions are implemented:

- `part_of_speech`:	Part-of-peech tagging and chunking on text
phrase_extract`:	Phrase extraction & named entity recognition on text
- `sentiment`:	Analyze the sentiment of text
- `sentimental`:	Tools to Work with the 'text-processing.com' API
- `stem`:	Perform word stemming on text

### TODO

- CRAN
- S-expression parser (convert string to a `list`)

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/sentimental")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(sentimental)

# current verison
packageVersion("sentimental")

```

### Test Results

```{r}
library(sentimental)
library(testthat)

date()

sentiment("hi friend")

stem("interestingly enough they overwhelmingly supported the wrong candidate")

part_of_speech("hello world")

phrase_extract("Maine is nice")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
